\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

To numerically compute \eqref{KineticProx}, we employ the proximal algorithm proposed in \cite{caluya2019TAC} with finite $N$ samples. Specifically, the proximal algorithm recursively updates probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$.

>>>>

To numerically compute \eqref{KineticProx}, we employ the proximal algorithm proposed in \cite{caluya2019TAC} with finite $N$ samples. Specifically, the proximal algorithm recursively updates probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N.$$
